Mood increases during video game play: A naturalistic observational case study of PowerWash Simulator

### 2023-09-05 ms.qmd
Reparameterize model

We analyzed the data with R [@rcoreteamLanguageEnvironmentStatistical2023] and used the brms package for models [@burknerBrmsPackageBayesian2017].

@@

model <- bf(mood | cens(cl) ~ 0 + post + (0 + post |p| pid) + (1 | ps)) +
  lf(sigma ~ 1 + (1 |p| pid)) +
  gaussian()

fit <- brm(
  model,
  data = dat,
  silent = 0,
  threads = 2,
  iter = 100,
  control = list(adapt_delta = .9),
  file = "models/brm-pre-post-location-scale"
)
summary(fit, prior = TRUE)
```

>>>>

@@

contrasts(dat$post) <- c(-0.5, 0.5)

model <- bf(mood ~ 1 + post + (1 + post | pid) + (1 | ps)) +
  gaussian()

fit <- brm(
  model,
  data = dat,
  silent = 0, # Required for printing mcmc progress on some systems
  threads = 2,
  iter = 500,
  control = list(adapt_delta = .95),
  file = "models/brm-pre-post-pid-ps"
)
```

```{r}
#| label: model-convergence
#| eval: false

hist(rhat(fit))
plot(fit)
pairs(fit$fit, pars = variables(fit)[1:7])
```

We analyzed the data with R [@rcoreteamLanguageEnvironmentStatistical2023] and used the brms package to estimate and post-process the models [@burknerBrmsPackageBayesian2017]. We used Stan's HMC sampler to draw `r number2(ndraws(fit))` samples from the posterior distribution, and used brms' default prior distributions on all parameters, and used numerical and graphical checks to ensure model convergence.
